Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-04-14 paper/abstraction/paper.tex
space edits

We evaluate \sysname by applying it on policies for backbone and data center networks. 
%We aim to evaluate the expressiveness of our abstractions, the precision of the abstract disjoint-path analysis, and the generation time of \sysname both with abstraction and without.

\subsection{Expressiveness and precision}

\begin{figure}[t!]
  \begin{center}
      \begin{tabular}{| l | c| c | c | c | c | }
      \hline
       & \textbf{Fixed} & \multicolumn{2}{|c|}{\textbf{Reachability}} & \multicolumn{2}{|c|}{\textbf{K-paths}} \\ \hline
       & & Some & All & Some & All \\
       & & Pairs & Pairs & Pairs & Pairs \\ \hline

@@

The top part of Figure~\ref{fig:analysis-precision} shows the results for common real-world settings: tree-based topologies coupled with valley-free routing.
We consider four variants of tree topologies: a standard fat tree~\cite{fattree}, the Facebook fat tree~\cite{facebook-fattree}, the F10 fault-tolerant fat tree~\cite{f10-fattree}, and VL2~\cite{vl2-fattree}. These variants differ in the number of tiers and the connectivity pattern between roles. For each, we use a tiered abstraction similar to that in our example (\S\ref{sec:overview}) and parameterize over the number of pods, which can be scaled for expansion. We report precision of both analyzing reachability and disjoint paths, and we report if \sysname is precise for all pairs of abstract nodes or only some of them. We record a check when the analysis is precise and a \Conserv{} when the analysis is conservative.

Our results are encouraging for these realistic settings. Our abstractions are perfectly expressive for all tree-based topologies---we did not have to fix any aspect of their structure---and the analysis is precise in all cases.

@@

To stress our abstractions and analysis, we consider additional topologies from the literature.

>>>>

%We evaluate \sysname on backbone and data center networks. 
%We aim to evaluate the expressiveness of our abstractions, the precision of the abstract disjoint-path analysis, and the generation time of \sysname both with abstraction and without.

\subsection{Expressiveness and precision}
\begin{figure}[t!]
  \begin{center}
\small
      \begin{tabular}{| l | c| c | c | c | c | }
      \hline
       & \textbf{Fixed} & \multicolumn{2}{|c|}{\textbf{Reachability}} & \multicolumn{2}{|c|}{\textbf{K-paths}} \\ \hline
       & & Some & All & Some & All \\
       & & Pairs & Pairs & Pairs & Pairs \\ \hline

@@

The top part of Figure~\ref{fig:analysis-precision} shows the results for common data center networks: tree-based topologies coupled with valley-free routing.
We consider four variants of tree topologies: a standard fat tree~\cite{fattree}, the Facebook fat tree~\cite{facebook-fattree}, the F10 fault-tolerant fat tree~\cite{f10-fattree}, and VL2~\cite{vl2-fattree}. These variants differ in the number of tiers and the connectivity pattern between roles. For each, we use a tiered abstraction similar to that in our example (\S\ref{sec:overview}) and parameterize over the number of pods, which can be scaled for expansion. We report precision of both analyzing reachability and disjoint paths, and we report if \sysname is precise for all pairs of abstract nodes or only some of them. We record a check when the analysis is precise and a \Conserv{} when the analysis is conservative.

Our results are encouraging for these settings. Our abstractions are perfectly expressive for all tree-based topologies---we did not have to fix any aspect of their structure---and the analysis is precise in all cases.

@@

%To stress our abstractions and analysis, we consider additional topologies from the literature.
